### 2015-05-13 whoop.tex
updates to optimisations

\medskip\noindent\textbf{Optimizations }
%
To increase precision we enhance \whoop with domain-specific knowledge of how the Linux kernel interacts with its drivers. This is an ongoing manual effort: the more drivers we study, the more domain-specific properties we discover, which we then exploit to make \whoop more precise. In our experience, one of the most effective precision optimizations is to enrich \whoop with information regarding kernel-imposed serialization. The Linux kernel can serialize calls to entry points, thus forcing them to run sequentially with each other. As an example, a large number of networking entry points are mutually serialized with RTNL, a network-specific kernel lock. \whoop exploits this knowledge and does not create pairs for entry points that are serialized.

>>>>

\medskip\noindent\textbf{Optimizations }
%
We have implemented various optimizations to increase the precision and performance of \whoop.

In our experience, one of the most effective precision optimizations is to enrich \whoop with information regarding \emph{kernel-imposed serialization}. The Linux kernel can serialize calls to entry points, thus forcing them to run sequentially with each other. As an example, a large number of networking entry points are mutually serialized with RTNL, a network-specific kernel lock. \whoop exploits this knowledge and does not create pairs for entry points that are serialized. This is an ongoing manual effort: the more drivers we study, the more such properties we discover, which we can then exploit to make \whoop more precise.
